---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# njmbase

<!-- badges: start -->
<!-- badges: end -->

The goal of njmbase is writing some personal use functions without any dependencies. Ideally,
these can be loaded onto an empty R session and immediately work without any other 
packages needed. 

## Installation

You can install the development version of njmbase from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nathaniel-morgan/njmbase")
```

## Example

Race allows you to find the difference in run time in second between two processes.
If the first process is faster the difference in time will be negative.

```{r example}
library(njmbase)
race(rnorm(1e5),rnorm(1e7))
race(rnorm(1e7),rnorm(1e5),simple = FALSE)
```

We can see that drawing more random numbers from rnorm takes more time.
